A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-15 text/formal-defnition.tex
Wrote a paragraph of evaluation context.

\begin{definition}[Evaluation Context]
	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$.
	In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
	\begin{align*}
		 & E^\varepsilon_B \in ECtx^\varepsilon_B ::= \square\ (\text{if\ } B = \varepsilon)
		\mid E^\varepsilon_B\ M \mid v^e\ E^\varepsilon_B \mid \TB_\alpha E^\alpha_B
		\mid \Lambda\alpha.E^\varepsilon_B \mid E^\varepsilon_B\ A'                                                                       \\
		 & E^A_B \in ECtx^A_B                     ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B \\
		 & \hspace{25mm} \mid E^\varepsilon_B \mid \TB_\alpha E^{A\alpha}_B \mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)      \\
		 & \hspace{25mm} \mid \Lambda\alpha.E^\varepsilon_B \mid E^A_B\ B' \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)        \\
	\end{align*}
\end{definition}

@@

\AI{some more explanation of the syntax of evaluation contexts.}

We write $E^A_B[M]$ for the term obtained by filling the hole in $E^A_B$ by $M$
and define the staged reduction relation.

\begin{definition}[Staged Reduction]
	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by
	the least relation closed under the rules below.
	% \begin{figure}
	% 	\begin{center}
	\begin{align*}
		E^A_\varepsilon [(\lambda x:\tau.M)\ v^\varepsilon] & \longrightarrow_s E^A_\varepsilon[M[x\mapsto v^\varepsilon]]      \\
		E^A_\varepsilon [(\Lambda\alpha.v^\varepsilon)\ A]  & \longrightarrow_s E^A_\varepsilon[v^\varepsilon[\alpha\mapsto A]] \\
		E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                            \\
	\end{align*}
	%    	\caption{Staged Reduction}
	%    	\label{fig:staged-reduction}
	%    \end{center}
	% \end{figure}
\end{definition}

>>>>

In order to define Staged Reduction, we define Redex and Evaluation Context.

@@

\begin{definition}[Evaluation Context]
	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$.
	In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
	\begin{align*}
		 & E^\varepsilon_B \in ECtx^\varepsilon_B ::= \square\ (\text{if\ } B = \varepsilon)
		\mid E^\varepsilon_B\ M \mid v^e\ E^\varepsilon_B \mid \TB_\alpha E^\alpha_B
		\mid \Lambda\alpha.E^\varepsilon_B \mid E^\varepsilon_B\ A'                                                                       \\
		 & E^A_B \in ECtx^A_B                     ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B \\
		 & \hspace{25mm} \mid E^\varepsilon_B \mid \TB_\alpha E^{A\alpha}_B \mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)      \\
		 & \hspace{25mm} \mid \Lambda\alpha.E^\varepsilon_B \mid E^A_B\ B' \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)        \\
	\end{align*}
\end{definition}
\AI{some more explanation of the syntax of evaluation contexts.}

We write $E^A_B[M]$ for the term obtained by filling the hole $\square$ in $E^A_B$ by $M$ 
and define the staged reduction relation.
Intuitively, $\square$ is the placefolder for redex.
Examples of evaluation context is below.
\red{Example of evaluation context}
% \begin{align*}
% \end{align*}

\begin{definition}[Staged Reduction]
	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by
	the least relation closed under the rules below.
	\begin{align*}
		E^A_\varepsilon [(\lambda x:\tau.M)\ v^\varepsilon] & \longrightarrow_s E^A_\varepsilon[M[x\mapsto v^\varepsilon]]      \\
		E^A_\varepsilon [(\Lambda\alpha.v^\varepsilon)\ A]  & \longrightarrow_s E^A_\varepsilon[v^\varepsilon[\alpha\mapsto A]] \\
		E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                            \\
	\end{align*}
\end{definition}

This reduction relation reduces a typed term in a unique way 
which is appropriate as call-by-value code generater.
It means that terms in brackets is not evaluated until the terms are run
and arguments of a function are evaluated before the application.
\red{Example of staged reduction}
